%%
% Resume | Jason Yao
%
% References:
% 		Debarghya Das (http://debarghyadas.com)
% %
\documentclass[]{hieudo-build}

% External Libraries
\usepackage{hyperref}

% Configuration Settings
\hypersetup{colorlinks=true,urlcolor=blue} % Turns the hyperlinks blue

\begin{document}

%%%%%%%%%%%%
% Header Section %
%%%%%%%%%%%%
\namesection{Jason Yao}
{
\normalsize % If you need to squeeze this to be smaller, set this to \small
\urlstyle{same}
	\faEnvelope \hspace{0.1cm} \href{mailto:JasonYao@nyu.edu}{JasonYao@nyu.edu}\\
	\faGithub \hspace{0.1cm} \href{https://github.com/JasonYao}{github.com/JasonYao}\\
	\faLinkedinSquare \hspace{0.1cm} \href{https://www.linkedin.com/in/JasonYaoNYU/}{linkedin.com/in/JasonYaoNYU}\\
    \faPhone \hspace{0.1cm} \href{tel:19493352639}{+1 (949) 335-2639} \\
    \faGlobe \hspace{0.1cm} \href{https://www.JasonYao.com}{JasonYao.com}
}

%%%%%%%%%
% Left column %
%%%%%%%%%
\begin{minipage}[t]{0.34\textwidth} 

%%
% Education
%%
\section{Education} 

\subsection{New York University}
\descript{College of Arts \& Science}
BA in Computer Science (CS) \\
Grad. May 2017 \\
\sectionsep

%% Turned off for US-based employers
%\subsection{Hong Kong International School}
%Grad. May 2013 \\
%\sectionsep

%%
% Skills
%%
\section{Skills}
\subsection{Programming}
\location{Programming Languages:}
Java, Python, C, JavaScript\\
Bash, Golang
\newline

\location{Big Data Tools:}
(Py)Spark + Yarn, AWS EMR, \\
AWS Batch, AWS Glue, \\
Hadoop
\newline

\location{Web Frameworks:}
Django, NodeJS, Express
\newline

\location{Databases:}
SQL: PostgreSQL, MySQL\\
noSQL: MongoDB
\newline

\location{Tools:}
git, vim, npm,\\
travisCI, AWS-cli
\newline

\sectionsep

\subsection{General}
\location{Languages (Native fluency):}
English, Mandarin
\newline

\location{Miscellaneous:}
I know how to learn, use Google, and read Stack Overflow.

\sectionsep

%%
% Activities
%%
\section{Activities}
Techwatch@MediaMath \\
Phi Kappa Sigma Fraternity \\
Tech@NYU \\
\sectionsep

%%
% Awards
%%
% \section{Awards} 
% Dean's List\\
% NYU PROMISE Scholarship\\
% Shelby C. Davis Scholarship\\
% President’s Circle Scholarship\\
% \sectionsep

%%
% Conference Talks \& Papers
%%
% \section{Conference Talks \& Papers} 
% Dean's List\\
% NYU PROMISE Scholarship\\
% Shelby C. Davis Scholarship\\
% President’s Circle Scholarship\\
% \sectionsep

%%
% Timestamp of resume generation
%%
\DTMsetdatestyle{mylastupdate}
\DTMdisplaydate{\the\year}{\the\month}{\the\day}{-1}

\end{minipage} 
\hfill
%%%%%%%%%%
% Right Column %
%%%%%%%%%%
\begin{minipage}[t]{0.65\textwidth} 

%%
% Experience
%%
\section{Experience}

% Note: All uses of \diffdate inside a \section, or \workplace
% requires a \protect in front, as discussed at:
% https://tex.stackexchange.com/questions/43127/error-with-newcommand-and-section/43130#43130
\workplace{MediaMath}{New York, NY}{\protect\diffdates{2017}{07}{\the\year}{\the\month}}
\position{Software Engineer II}{Oct. 2017 – Present}

 \vspace{\topsep} % Hacky fix for awkward extra vertical space
 
\begin{tightemize}
\item {\bf Lead contributor} to a company-critical ETL service responsible
for {\bf generating all fee data used by thousands of advertising bidders world-wide}.
\item {\bf Reduced client friction by 75\%}, and increased company's potential
revenue substantially by enabling individual feature pricing.
\item {\bf Increased team developer velocity by 300\%} (based on story point
completions before/after) by creating a command-line API interacting
with service subsystems
\item Continued assuming SDE II responsibilities from before, increasing team cohesion,
technical ability, and the implementation of positive feedback loops for the team.
\item Increased the reliability and consistency of the service by building in
monitoring and resiliency fallbacks compliant with the Service Level
Objective established in partnership with PMs.
\end{tightemize}
\sectionsep

\position{Software Engineer I}{Jul. 2017 – Oct. 2017}

\vspace{\topsep} % Hacky fix for awkward extra vertical space

\begin{tightemize}
\item Designed \& built out mission-critical internal financial platforms depended upon by the core of the company (responsible for over 70\% of company revenue), 
\item Took on responsibilities of an SDE II early on, contributing to increasing team cohesion, technical ability, and the implementation of positive feedback loops for the team.
\end{tightemize}
\sectionsep

\workplace{Ivy Tech Capital}{Beijing, China}{\protect\diffdates{2016}{06}{2016}{08}}
\position{Software Engineer Intern}{Jun. 2016 – Aug. 2016}

\vspace{0.9em} % Hacky fix for awkward extra vertical space

\begin{tightemize}
\item Created presentable {\bf fantasy sports web service} MVP to
incubator investors, winning an award for "Best Potential for Unicorn"
by the judging panel. Built using Python \& the Django web framework.
\end{tightemize}
\sectionsep

\workplace{Phi Kappa Sigma}{New York, NY}{\protect\diffdates{2015}{01}{2017}{05}}
\position{Technology Chair}{Jan. 2015 – May 2017}

\vspace{\topsep} % Hacky fix for awkward extra vertical space

\begin{tightemize}
\item Designed, developed, and maintained the 
{\bf \href{https://www.skullhouse.nyc}{organization website}} and 
\href{https://github.com/JasonYao/Bobst-Room-Automator}{tools}
\end{tightemize}
\sectionsep

%%
% Organisations
%%
%\section{Organisations}
% \runsubsection{The Westminster News} \\
% \descript{Co-Editors-in-Chief (2014) | Layout Editor (2012) }
% \location{Sep 2012 – May 2015 | Simsbury, CT}
% \begin{tightemize}
% \item Led 30+ staff at a 400-student boarding school to publish the monthly school newspaper.
% \item Consulted in layout design and technology application.
% \end{tightemize}
% \sectionsep

% \runsubsection{VietAbroader Organization} \\
% \descript{Program Assistant Manager | VAPedia Associate }
% \location{Mar 2013 – Mar 2014 | Ho Chi Minh City, Vietnam}
% \begin{tightemize}
% \item VietAbroader is a non-profit organization run by Vietnamese students abroad.
% \item Designed the high school content for the VAPedia website.
% \item Assisted in recruiting guest speakers and volunteers for VietAbroader Study-Abroad Conference 2013.
% \end{tightemize}
% \sectionsep

%%
% Projects
%%
\section{Projects}
\runsubsection{Java -> C++ Transpiler}
\descript{New York, NY, 2016 Fall}
{\bf Team Leader} of 5 tasked with building a transpiler in Java. Used SBT to build, JUnit for testing, and visitor + delegator design patterns. *
\sectionsep

%\runsubsection{QR Item Finder}
%\descript{}
%\location{New York, NY, 2015 Fall}
%{\bf Technical Lead} of 4 that built a \href{https://github.com/JasonYao/Large-Scale-Final-Project-Lost-and-Found-Recovery-Service}{QR item finder service} with a focus on scalability. Used Django, MySQL, Nginx, and memcached.
%\sectionsep

%\runsubsection{Meeter}
%\descript{}
%\location{New York, NY, 2017 Spring}
%\href{https://github.com/JasonYao/university-video-meeter}{Chat webapp} using Node, Express, MongoDB, AWS-S3, socket.io, and a  WebRTC library to connect university and high school students. (in progress)\\
%\sectionsep

* Repo access available upon request
\end{minipage}

% TODO P2: Remove after
%\newpage
%\tableofcontents
\end{document}